Project Notes - Installability

### 2021-06-24 StateOfPractice/Peter-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
updated LBM domain expert presentation 2

\bi
\item May use parallel processing
\item Different equilibrium distribution functions
\item Coefficients for equilibrium distribution function (based on velocity directions)
\item Lattice dimensions (1D, 2D, 3D)
\item Varied velocity directions, partially based on dimensions 
\item Collision operators (SRT, TRT, MRT, BGK)
\item Collision vs collision-free transport equations
\item Number of fluid that can be modeled simultaneously
\item Fluid parameters (Reynolds Num., density, viscosity, etc.)
\item Lattice boundary (reflective or non-reflective)
\ei

>>>>

\bi
\item May use parallel processing (May use varied tools for this - MPI, CUDA..)
\item Different equilibrium distribution functions (compressible and incompressible)
\item Coefficients for equilibrium distribution function (based on velocity directions - 2,3,5,9,13,15,19,27)
\item Lattice dimensions (1D, 2D, 3D)
\item Varied velocity directions, partially based on dimensions (2,3,5,9,13,15,19,27)
\item Collision operators (SRT, TRT, MRT, BGK)
\item Collision vs collision-free transport equations
\item Number of fluids that can be modeled simultaneously
\item Fluid parameters (Reynolds Num., density, viscosity, etc.)
\item Lattice boundary (reflective or non-reflective)
\ei
